REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-11-29 main.tex
completed comments on main text

We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SNIa begins to make a significant contribution to the galactic chemical evolution. This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the \textbf{170} Myr simulated here. % The origin of this feature and the longer term chemical evolution of this galaxy will be investigated in a future work.

@@

\subsection{Missing Physics}
Although we include detailed physics in our simulations, there remains additional physics that may be relevant.These are discussed below.

\subsubsection{Full Stellar Wind Model}
\label{sec:stellar winds discussion}
As discussed previously, our stellar wind model significantly reduces the injected wind velocity from $\sim$1000 km s$^{-1}$ to 1 km s$^{-1}$. Although our model is capable of generating realistic stellar winds with temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical. When considered in isolation, stellar winds are an important source of pre-SN feedback and do dramatically influence the dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}. However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or GMCs \citep{Dale2014}. They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}. Although they likely have minimal dynamical importance, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.

@@

\subsubsection{Cosmic Rays and Magnetic Fields}
Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017} and simulations of both isolated \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017} and cosmological galaxies \citep{SalemBryanHummels}. These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows with different phases and velocities than those driven through stellar feedback alone \citep{SalemBryanCorlies}. Modeling cosmic rays is challenging, however, as they encompass a wide range of energies (give range), with significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}. Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy. In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM. Modeling cosmic ray feedback completely requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena. Finally, including MHD presents additional difficulties in untangling the effects each individual feedback mechanism on galaxy chemodynamics.

>>>>

We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SN Type Ia begins to make a significant contribution to the galactic chemical evolution. This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the \textbf{170} Myr simulated here. % The origin of this feature and the longer term chemical evolution of this galaxy will be investigated in a future work.

@@

\subsection{Missing Physics}
Although we include detailed physics in our simulations, there remains additional physical processes that may be relevant.These are discussed below.

\subsubsection{Full Stellar Wind Model}
\label{sec:stellar winds discussion}
Our stellar wind model significantly reduces the injected wind velocity from $\sim$1000 km s$^{-1}$ to 1 km s$^{-1}$. Although our model is capable of generating realistic stellar winds with temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical. When considered in isolation, stellar winds are an important source of pre-SN feedback and do dramatically influence the dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}. However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or 
%mm GMCs
   individual giant molecular clouds
\citep{Dale2014}. They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}. Although they likely have minimal dynamical importance
%mm 
   at resolutions where peak densities are not anyway high enough to trap ionization 
   fronts, 
a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.

@@

\subsubsection{Cosmic Rays and Magnetic Fields}
Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}. These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through 
%mm stellar [CRs are also stellar feedback...]
     thermal 
feedback alone \citep{SalemBryanCorlies}. Modeling cosmic rays is challenging, however, as they encompass a wide range of energies (give range), with significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}. Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy. In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM. Modeling cosmic ray feedback completely requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena. Finally, including MHD presents additional difficulties in untangling the effects each individual feedback mechanism on galaxy chemodynamics.
